---
title: "Reproducable Pitch Presentation - randomized normal distribution"
author: "Karan Shishoo"
date: "May 25, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(size = "tiny")
```

## Intoduction

This is a Reproducable Pitch Presentation, which is part 2 of the final project under developing data products course of John Hopkins on Coursera. The first part of this project had us develop and publish a shiny app which took an input from the user and provided an output using that input. 

The application is hosted on shinyapps.io and can be accessed from [here](https://kshishoo.shinyapps.io/my_first_web_app/)

The files (ui.R and server.R) are hosted on github and they can be found [here](https://github.com/karan-shishoo/Developing-Data-Products/tree/master/web_app/my_first_web_app)

## Usage

This application allows the user to set a few properties of a random normal distribution

- the number of datasets
- the variance
- the mean

It also allows them to  set the number of bins of the resultant histogram.

The idea of the application is to allow people to visualize how the output of a random normal distribution changes as these variables are changed.

## How the execution looks
The Sidebar Panel is setup to take in 4 inputs from the user (with default values set for each input) which are then used by the server as shown below

```{r r.ui, include=TRUE,echo=TRUE, eval=FALSE, tidy=FALSE, size="tiny"}
output$distPlot <- renderPlot({
    # generate bins based on input$bins from ui.R
    x    <- rnorm(input$xnum, input$xmean, input$xvar)
    bins <- seq(min(x), max(x), length.out = input$bins + 1)
    
    # draw the histogram with the specified number of bins
    hist(x, breaks = bins, main = "Normal Distribution",
         col = 'darkgray', border = 'white')
```

## How the Output looks
below is an example output assuming some inputs
```{r server.r, include=TRUE,echo=TRUE,warning=FALSE,message=FALSE}
library(plotly); x <- rnorm(100,0,20); bins <- 20; hist(x, breaks = bins,
  main = "Normal Distribution", col = 'darkgray', border = 'white')
```
